Software Citation Principles

### 2016-07-21 sc-principles/rebuttal/rebuttal.tex

\item \textbf{Reviewer comment:}
\emph{Lines 32--35: as a justification for treating software differently from data, I found this passage raised more questions than answers, and that the comments here were uncompelling and unsupported. For example, some published data is updated on a frequency comparable with some software (e.g. the bi-monthly release schedule of FlyBase is comparable with many software projects - \url{http://flybase.org/static_pages/docs/release_schedule.html}). Also, I think the distinction between data and software is less clear-cut than the authors suggest (e.g. is a schema or stylesheet data or software?). I would see the difference between software and data as more akin to the difference between research methods and research findings, but that is just a personal opinion. My suggestion would be that this justification is not really necessary to the overall purpose of the paper, and might be dropped without significant loss of value.}

\textbf{Our response:}

\niemnote{I think we all would agree that software is a research method and data are research findings, but I do think we need some explanation of the differences---if only to justify why software citation may be different than data citation}

\niemnote{Dan: work on this. Bring in text from CodeMeta paper and your blog post.} \katznote{done - and see suggested response below}

We respectfully disagree with the reviewer about the value of this section. Since our work on software citation is being done following previous work on data citation (including the PeerJ CS paper on data citation (\url{https://peerj.com/articles/cs-1/}), and since our software citation principles have some difference from the data citation principles, we feel it is important to explain the high level reasons why differences might be expected.  We do agree with the reviewer's specific point about release frequency, and have added a note about this.  We have also expanded the set of differences to make the case more convincing.

### 2016-07-21 sc-principles/software-citation-principles.tex
fixing bullet in table to match text in B.7 Adding description in B.7 to match what was already in the Google Doc Suggesting that we merge B.7 with B.1, as suggested in Google Doc
changing text in 6.1 about citation vs provenance in response to reviewer 2 point 10, and changing the rebuttal to match

7.\ Benchmark software                           & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & + & + &             & Researcher, software engineer \\

@@

Note that some software which is or could be captured as part of data provenance may not be cited.
Citation is a record of software that is important to a research outcome, where provenance is a record of all steps (including software) used to generated particular data within the research process.
This implies that for a data research product, provenance data will include all cited software, but not necessarily vice versa.
Similarly, the software metadata that is recorded as part of data provenance should be a superset of the metadata recorded as part of software citation.
The data recorded for reproducibility should also be a superset of the metadata recorded as part of software citation.
These statements may also be true for software products.
In general, we intend the software citation principles to cover the minimum of what is necessary for software citation for the purpose of software identification.
%Other use cases (e.g., provenance, reproducibility) may lead to additional requirements (i.e., enhanced metadata).
%\niemnote{Perhaps rephrase to ``
Some use cases related to citation (e.g., provenance, reproducibility) might have additional requirements beyond the basic metadata needed for citation, as Table~\ref{tab:use_cases} shows.
%''}
%\ssnote{from the data side, an example might be found in the National Climate Assessment (NASA, GCIS) where this is captured in PROV instead?}
%\dmnote{ Mention that the principles are covering what's necessary, not necessarily what is sufficient for a given use case. So perhaps we should discuss things like configurations or bugs? }

@@

>>>>

7.\ Benchmark software                           & \textbullet & \textbullet &  \textbullet  &             & \textbullet & \textbullet & \textbullet &             & + & + &             & Researcher, software engineer \\

@@

Note that some software which is or could be captured as part of data provenance may not be cited.
Citation is partly a record of software that is important to a research outcome\footnote{Citation can be used for many purposes, including for software: which software has been used in the work, which software has influenced the work, which software is the work superseding, which software is the work disproving, etc.}, where provenance is a record of all steps (including software) used to generated particular data within the research process.
This implies that for a data research product, provenance data will include some of the cited software.
Similarly, the software metadata that is recorded as part of data provenance should be a superset of the metadata recorded as part of software citation for the software that was used in the work.
The data recorded for reproducibility should also be a superset of the metadata recorded as part of software citation.
These statements may also be true for software products.
In general, we intend the software citation principles to cover the minimum of what is necessary for software citation for the purpose of software identification.
%Other use cases (e.g., provenance, reproducibility) may lead to additional requirements (i.e., enhanced metadata).
%\niemnote{Perhaps rephrase to ``
Some use cases related to citation (e.g., provenance, reproducibility) might have additional requirements beyond the basic metadata needed for citation, as Table~\ref{tab:use_cases} shows.
%''}
%\ssnote{from the data side, an example might be found in the National Climate Assessment (NASA, GCIS) where this is captured in PROV instead?}
%\dmnote{ Mention that the principles are covering what's necessary, not necessarily what is sufficient for a given use case. So perhaps we should discuss things like configurations or bugs? }

@@

\katznote{I think we should merge this with B.1, as suggested in the google doc - the bullets are all the same}
